---
title: "Homework_4_SecondTry"
author: "Jacob Coggshall"
date: "2023-05-27"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Loading In Packages

```{r}
library(tidyverse)
library(naniar)
library(here)
library(janitor)
library(ggplot2)
library(dplyr)
library(gridExtra)
```

```{r}
fishdata <- read.csv(
  here("data", "ntl6_v12.csv"))|>
  clean_names()|>
  filter(spname == "TROUTPERCH") |>
  filter(!is.na(weight))
```

### Biological terms:
H0: Fish length does not predict fish weight for trout perch across all sample years.
HA: Fish length predicts fish weight for trout perch across all sample years.

### Standard
Null hypothesis (H0): There is no significant relationship between fish length (L) and fish weight (W) for trout perch across all sample years.

Alternative hypothesis (HA): There is a significant relationship between fish length (L) and fish weight (W) for trout perch across all sample years.

### Mathmatical
H0: The coefficient of fish length in the linear regression model is equal to zero.
HA: The coefficient of fish length in the linear regression model is not equal to zero.


# Checking missing variable
```{r}
gg_miss_var(fishdata)
```

The missing data is not relevant to our hypotheses because we have filtered out all the rows where there was no reading for the weight of trout perch. By removing the rows with missing weight values, we ensure that our analysis includes only complete data points, allowing us to examine the relationship between fish length and fish weight without the confounding effect of missing values.



```{r}
t_test_result <- t.test(fishdata$length, fishdata$weight)

t_test_result
```

```{r}
cor_result <- cor.test(fishdata$length, fishdata$weight)

print(cor_result)
```

# Testing Linearity

```{r}
linear <- ggplot(data = fishdata, aes(x = length, y = weight)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(x = "Fish Length", y = "Fish Weight",
       title = "Plot of Fish Length vs. Fish Weight")
```

# Testing Normalilty

```{r}
# Create a histogram
histo <- ggplot(data = fishdata, aes(x = weight)) +
  geom_histogram(binwidth = 1, fill = "lightblue", color = "black") +
  labs(x = "Fish Weight", y = "Frequency",
       title = "Histogram of Fish Weight")

# Create a Q-Q plot
qq <- ggplot(data = fishdata, aes(sample = weight)) +
  stat_qq() +
  stat_qq_line() +
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles",
       title = "Q-Q Plot of Fish Weight")
```

# Testing Homoscedasticity

```{r}

# Fit a linear regression model
lm_model <- lm(weight ~ length, data = fishdata)

# Extract the residuals and predicted values
residuals <- lm_model$residuals
predicted_values <- predict(lm_model)

# Create a data frame with predicted values and residuals
residual_df <- data.frame(Predicted = predicted_values, Residuals = residuals)

# Create a scatter plot of residuals against predicted values
scatter <- ggplot(data = residual_df, aes(x = Predicted, y = Residuals)) +
  geom_point() +
  labs(x = "Predicted Values", y = "Residuals",
       title = "Residuals vs. Predicted Values Plot")

```

```{r}
# Load the necessary packages
library(gridExtra)

# Arrange the plots in a grid layout
full_grid <- grid.arrange(qq, scatter, histo, linear,ncol = 2, nrow = 2, widths = c(5, 7))
```

The scatter plot with a trendline shows the relationship between fish length and fish weight. By visually analyzing the plot, we can observe the general trend and determine that there is a positive or negative correlation between the two variables.


The scatter plot of residuals against predicted values shows the distribution of the residuals across the range of predicted values. By examining the plot, we can assess that there is no significant deviation in the residuals.

The histogram of fish weight displays the frequency distribution of fish weights, allowing us to observe the distribution's shape and any potential outliers. After examining the plot, we can determine the data is skewed to the left, indicating generally lower weights.


The Q-Q plot compares the observed fish weight data to a theoretical normal distribution. If the data points fall approximately along a straight line, it suggests that the data follows a normal distribution. Deviations from the straight line may indicate departures from normality or systematic biases in the data.This dat looks generally normally distributed

```{r}
summary(fishdata)
```

```{r}
# Fit a linear regression model
model <- lm(weight ~ length, data = fishdata)

# Print the model summary
summary(model)
```


The data analysis, based on 290 observations from eleven primary lakes (Trout, Perch), revealed that fish length significantly predicts fish weight. The regression model showed a strong positive relationship between fish length and weight, with length explaining approximately 81.58% of the variability in weight. The findings suggest that as fish length increases, their weight tends to increase as well.

```{r}
# Perform ANOVA
anova_result <- aov(weight ~ length, data = fishdata)

# Generate ANOVA table
anova_table <- summary(anova_result)

# Print the ANOVA table
print(anova_table)
```

```{r}
# Perform ANOVA
anova_result <- aov(weight ~ length, data = fishdata)

# Extract ANOVA table
anova_table <- broom::tidy(anova_result) %>%
  select(df, sumsq, meansq, statistic, p.value) %>%
  clean_names()

# Format p-values without scientific notation
anova_table$p_value <- format.pval(anova_table$p_value, digits = 3)

# Rename columns
colnames(anova_table) <- c("Source", "DF", "Sum_Sq", "Mean_Sq", "F_Value", "P_Value")

# Print the summary table
print(anova_table)

#summary
summary(fishdata)
```


The ANOVA table provides statistical information on the relationship between fish length and weight, indicating that there is a significant relationship between these variables (p-value < 2.2e-16). The summary object provides additional details such as the coefficient estimates, standard errors, t-values, and confidence intervals for the regression model. Both the ANOVA table and the summary object support the conclusion that fish length is a significant predictor of fish weight.

```{r}
# Create a scatter plot of the underlying data
scatter_plot <- ggplot(data = fishdata, aes(x = length, y = weight)) +
  geom_point() +
  labs(x = "Fish Length", y = "Fish Weight") +
  theme_minimal()

# Add model predictions and confidence intervals
model_plot <- scatter_plot +
  geom_smooth(method = "lm", se = TRUE, fill = "lightblue", color = "blue") +
  theme_minimal()

# Display the final plot
model_plot
```

Caption: Scatter plot showcasing the relationship between fish length and weight. The upward-sloping blue line indicates a positive correlation, suggesting that as the length of the fish increases, so does its weight. The shaded light blue areas surrounding the line represent the confidence intervals, indicating the range of plausible weight values for a given length. The plot suggests a strong and consistent association between fish length and weight, providing evidence for the predictive power of length in estimating the weight of trout and perch in the studied population.